---
title: Basic Plots
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    self_contained: true
    vertical_layout: scroll
    theme: spacelab
    source: embed
---

```{r}
knitr::opts_chunk$set(cache = TRUE, fig.align = 'center')

library(ggplot2)
library(ggthemes)
library(ggsci)

library(dplyr)

library(wordcloud)
library(tm)

```

# {.sidebar data-width=150}

#### Packages

* [ggplot2](https://ggplot2.tidyverse.org/reference/index.html)

* [ggsci](https://cran.r-project.org/web/packages/ggsci/vignettes/ggsci.html)

* ggthemes

* scales

* ggradar

* tm

* wordclouds

* dplyr

* plotly


# Data 

##

### Dataset

```{r}

data("mtcars")
DT::datatable(mtcars)

```

##

### Description

The data was extracted from the 1974 _Motor Trend US magazine_, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

A data frame with 32 observations on 11 (numeric) variables.

**mpg**	 Miles/(US) gallon

**cyl**	 Number of cylinders

**disp**	 Displacement (cu.in.)

**hp**	 Gross horsepower

**drat**	 Rear axle ratio

**wt**	 Weight (1000 lbs)

**qsec**	 1/4 mile time

**vs**	 Engine (0 = V-shaped, 1 = straight)

**am**	 Transmission (0 = automatic, 1 = manual)

**gear**	 Number of forward gears

**carb**	 Number of carburetors



# Bar plot 

## 

### Simple

```{r barplot1}

ggplot(mtcars, aes(cyl)) + 
  geom_bar(color = I("black"), fill = I("darkcyan")) +
    xlab("Number of cylinders in a car") +
      ylab("Number of cars")
  
```

##
### Stacked

```{r barplot2}
ggplot(mtcars, aes(cyl)) + 
  geom_bar(color = I("black"), aes(fill = factor(am))) +
    xlab("Number of cylinders in a car") +
      ylab("Number of cars")+
        labs(fill = "Transmission")+
          scale_fill_uchicago("dark")
```



# Histogramm
##
### 

```{r}
ggplot(mtcars, aes(hp)) +
  geom_histogram(color = I("black"), aes(fill = ..count..), binwidth = 25) +
    xlab("Horsepower") +
      ylab("Number of cars")
```

##

# Pie Chart

##

### Simple

```{r piechart}

ggplot(mtcars, aes(x = 1, y = sort(carb), fill = factor(sort(carb)))) +
  geom_bar(stat = "identity") +
      coord_polar(theta = "y") + labs(y = "Carburators", fill = "") +
      
      theme(
            axis.line=element_blank(),
            axis.text.x=element_blank(),
            axis.text.y=element_blank(),
            axis.ticks=element_blank(),
            axis.title.y=element_blank(),
            panel.background=element_blank())+
          
              scale_fill_aaas()

```

##
### Labeled

```{r}
# calculate a number of carbs in each group of cars with 2, 3, 4, ... carbrators
mt = mtcars %>% select(carb) %>%
  mutate(carbFactor = factor(carb)) %>%
    arrange(carbFactor) %>% 
      group_by(carbFactor) %>%
        mutate(numCarbs = sum(carb))

# how much carburators in each group in %
mt = as.data.frame(mt)
mt$fracCarbs = round(mt$numCarbs/cumsum(mt$carb)[length(mt$carb)]*100, 1)

# select each group once for labeling
mt1 = as.data.frame(unique(mt))

ggplot(mt, aes(x = 1, y = carb) ) + 
  geom_bar(stat = "identity", aes(fill = carbFactor))+
    geom_text(data = mt1, aes(x = 1.2, y = 94 - cumsum(numCarbs), 
                             label = paste0(fracCarbs,"%")), size = 5) +
      
        coord_polar(theta = "y") + labs(y = "Carburators", fill = "") +
  
          theme( 
                axis.line=element_blank(),
                axis.text.x=element_blank(),
                axis.text.y=element_blank(),
                axis.ticks=element_blank(),
                axis.title.y=element_blank(),
                panel.background=element_blank()) +
  
                    scale_fill_aaas()

```


# Scatter Plots

##

### Simple 


```{r scatt}
ggplot(mtcars, aes(mpg, wt)) +
  geom_point(aes(col = factor(cyl)), shape = 16, size = 4)+
    xlab("Miles/(US) gallon") +
      ylab("Weight (1000 lbs)") +
        labs(color = "Cylinders") +
          scale_color_aaas()

```

##

### With Regression Line

```{r scattregr}

ggplot(mtcars,aes(x=mpg,y=wt,color = factor(cyl)) ) + geom_point(shape = 16, size = 4) +
  geom_smooth(method="lm", se= TRUE, color = "red") + xlab("Miles per Gallon ") +
  ylab("Weight") + labs(colour = "Cylinders") + scale_color_aaas()

```


# Lines
##
### Multiple Layers + Legend

```{r lines}

data("EuStockMarkets")
EuStock <- as.data.frame(EuStockMarkets)

all_stocks <- ggplot() +
  geom_line(data = EuStock,aes(x=c(1:nrow(EuStock)), y = DAX, color = 'DAX'), 
            size=1)+
  
  geom_line(data = EuStock,aes(x=c(1:nrow(EuStock)), y = SMI, color='SMI'), 
            size =1)+
  
  geom_line(data = EuStock,aes(x=c(1:nrow(EuStock)), y = CAC, color = 'CAC'), 
            size =1) +
  
  geom_line(data = EuStock,aes(x=c(1:nrow(EuStock)),y = FTSE, color = 'FTSE'), 
            size =1) + 
  
  labs(x = "Days", y = "Price", colour = "Markets") + 
  
  scale_colour_aaas(guide = guide_legend(reverse = TRUE))
  
all_stocks
  
```

##

### Stock Markets Data

Daily Closing Prices of Major European Stock Indices, 1991–1998

```{r stockdata}
DT::datatable(EuStock)
```



# Word Clouds

##

### Centered

```{r wordcloud}

# download file
#download.file("https://ibm.box.com/shared/static/cmid70rpa7xe4ocitcga1bve7r0kqnia.txt",
#              destfile = "./Data/churchill_speeches.txt", quiet = TRUE)


# Load the data as a corpus

dirPath <- "./Data/wordcloud"  
speech <- Corpus(DirSource(dirPath))

# inspect the content
#inspect(speech)

# Data cleaning

# Convert the text to lower case
speech <- tm_map(speech, content_transformer(tolower))

# Remove numbers
speech <- tm_map(speech, removeNumbers)

# Remove english common stopwords
speech <- tm_map(speech, removeWords, stopwords("english"))

# Remove your own stop word
# specify your stopwords as a character vector
speech <- tm_map(speech, removeWords, c("floccinaucinihilipification", "squirrelled"))

# Remove punctuations
speech <- tm_map(speech, removePunctuation)

# Eliminate extra white
speech <- tm_map(speech, stripWhitespace)

# Create a Term Ducument Matric
dtm <-TermDocumentMatrix(speech)


# Convert to matric
m <- as.matrix(dtm)

# Sort
v <- sort(rowSums(m), decreasing = TRUE)

# Transform to a data frame
d <- data.frame(word = names(v), freq = v)

wordcloud(words = d$word, freq = d$freq, scale=c(5,.1), min.freq = 1, max.words = 175,
          colors=brewer.pal(8, "Dark2"),
          random.order = FALSE)

```

##

### Random

```{r wordcloud1}

wordcloud(words = d$word, freq = d$freq, scale=c(5,.1), min.freq = 1, max.words = 175,
          colors=brewer.pal(8, "Dark2"),
          random.order = TRUE)
```

###

[Text](https://ibm.box.com/shared/static/cmid70rpa7xe4ocitcga1bve7r0kqnia.txt)


# Radar Charts

##

###

```{r radarlibraries}
# download from the GitHub repository of the developer, Ricardo Bion
# devtools::install_github("ricardo-bion/ggradar", dependencies=TRUE)

library(ggradar)
library(scales)

```

```{r radardata}

#Select our dataset
mtcars %>%
  
  #atribute rownames to a variable
  add_rownames( var = "group" ) %>%
  
    #assign each variable -- car names -- to their related variables
      mutate_each(funs(rescale), -group) %>%
  
        #select which data to plot
        head(3) %>% select(1:10) -> mtcars_radar

```

```{r radarchart, fig.height=6, fig.width=9}

options(warn=-1)
ggradar(mtcars_radar)

```

##


# Box Plots

##

###

```{r boxplot}

ggplot(mtcars, aes(factor(cyl), mpg)) + 
    geom_boxplot(aes(fill = factor(cyl)) )+
        xlab("Cylinders") + ylab("Miles per Gallon") +
            scale_fill_aaas() + 
                #remove legend
                theme(legend.position="none")

plotly:: ggplotly()

```

##


# Maps

##

### European Union

```{r ggplotmap}

states = read.csv("./Data/states.csv")

worldMap <- map_data("world")

states2 <- states %>% filter(European.Union == "Member") %>% 
  mutate(Country = as.character(Country))

worldMap1 <- worldMap %>% 
  mutate(region = ifelse(region == "UK", "United Kingdom", region)) %>%
    arrange(desc(region) )

worldMap2 <- worldMap1 %>% filter(region %in% states2$Country)

europMap <- left_join(worldMap2, states2, by = c("region"="Country"))


ggplot(europMap, aes(x = long, y = lat, group = group, fill = factor(Accession.Year)) ) + 
  geom_polygon(color = "black") + labs(fill = "Accession Year") +
  theme( 
    axis.line=element_blank(),
    axis.text.x=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks=element_blank(),
    axis.title.y=element_blank(),
    axis.title.x=element_blank(),
    panel.background=element_blank()) +
  
  scale_fill_aaas()
```

##

### Euro Zone

```{r ggplotmap2}

ggplot(europMap, aes(x = long, y = lat, group = group, 
                     fill = factor(ifelse(Currency == 'Euro', 'Euro', 'Non-Euro'))) ) + 
  geom_polygon(color = "black") + labs(fill = 'Zone') +
  theme( 
    axis.line=element_blank(),
    axis.text.x=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks=element_blank(),
    axis.title.y=element_blank(),
    axis.title.x=element_blank(),
    panel.background=element_blank()) +
  
  scale_fill_aaas()
  

```
